{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA

### 2021-11-26 paper/tex/sections/conclusion.tex
conclusion proofread

     \item \textbf{Detections by type:} Specifically, our fiducial model predicts a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs. The errors quoted here are the $1$-$\sigma$ Poisson uncertainties resulting from the random initialisation of the Milky Way (see Table~\ref{tab:detection_rates}).

    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope phase, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions. However, uncertainties related to the efficiency of mass transfer, the remnant mass prescription, the maximum neutron star mass and PISN have little effect on the detection rates (see Fig.~\ref{fig:detection_rates})

>>>>

     \item \textbf{Detections by type:} For our fiducial model, we predict a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs. The errors quoted here are the $1$-$\sigma$ Poisson uncertainties resulting from the random initialisation of the Milky Way (see Table~\ref{tab:detection_rates}).

    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions. However, uncertainties related to the efficiency of mass transfer, the remnant mass prescription, the maximum neutron star mass and PISN have little effect on the detection rates (see Fig.~\ref{fig:detection_rates})
